Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-05-03 ms.tex
I did some word changes such as long to short wavelength and other clarifications on the first few pages suggested by Lisa May.

\title{Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short Wavelength Dispersed Hartmann Sensor}

@@

\author{E. Schlawin \and M. Rieke? \and J. Leisenring \and J. Fraine? \and D. Kelly \and L. M. Walker? \and K. Misselt}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

@@

\begin{abstract}
James Webb Space Telescope (JWST) offers unprecedented sensitivity, stability and wavelength coverage for transiting exoplanet studies, opening up new avenues for measuring atmospheric abundances, structure and temperature profiles. Taking full advantage of JWST spectroscopy of planets from 0.6 $\mu$m to 28$\mu$m, however, will require many observations with a combination of the NIRISS, NIRCam, NIRSpec and MIRI instruments. In this white paper, we discuss a new NIRCam mode (not yet approved and implemented) that can reduce the number of observations needed for observations in the 1.0$\mu$m to 5.0$\mu$m wavelength range. The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments. NIRCam's long wavelength arm includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R \sim 1770$ and it has already been approved for wide field slitless spectroscopy. We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short wavelength arm. This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spectra for every source at $R \sim \DHSres$. The DHS can observe the brightest host stars of any JWST mode. We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres. The DHS essentially comes for free with any NIRCam long wavelength grism observation, but the readout has to be selected to ensure that the long wavelength grisms observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink.
\end{abstract}

@@

The James Webb Space Telescope (JWST) \citep[e.g.][]{gardner2006SSRv} has the potential to profoundly expand and deepen the science of transiting exoplanets \citep[e.g.][]{greene2016jwst_trans}. The wavelength coverage from 0.6$\mu$m to 28$\mu$m ads significantly to the wavelengths covered by the Hubble Space Telescope (currently 0.09$\mu$m to 1.7$\mu$m). Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent observatory for characterizing the atmospheres of planets that transit their host stars with time series observations. Ground-based observatories and the Hubble Space Telescope (HST) have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}. JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to it host star. Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes at longer wavelengths.

No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum over these wavelengths. The largest bandwidths possible are NIRSpec's low resolution prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m. Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments. For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7 $\mu$m to 12 $\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7 to 2.5$\mu$m), two with NIRCam's Long Wavelength Arm (2.44$\mu$m to 4.98 $\mu$m) \footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m). With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours. This was calculated with the Astronomer's Proposal Tools software\footnote{http://www.stsci.edu/hst/proposing/apt} with the NIRISS SOSS mode, NIRCam's F322W2 and F444W grism time series and the MIRI Low Resolution spectrograph (LRS).

The NIRCam instrument was originally designed as an imager, but it includes several spectroscopic modes originally designed for wavefront sensing. These include the grisms installed in its long wavelength arm as well as the Dispersed Hartmann Sensors (DHSs) installed in its short wavelength arm. The long wavelength grisms are used in concert with broadband filters. The F322W2 filter encompasses 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter encompasses 3.88$\mu$ to 4.98$\mu$m at half maximum throughput. These filters and grism are enabled and supported JWST science modes. The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput. The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the first order of the spectrum begins to overlap at at 2.0$\mu$m.

The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5 $\mu$m. This is because the instrument has a dichroic that splits the incoming beam into a short wavelength arm and long wavelength arm, so simultaneous imaging and spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths. In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter. Thus, the DHS data comes ``for free'' with any long wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}. For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0 to 2.4$\mu$m and higher Signal to Noise ratios from NIRISS are not required. The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long wavelength NIRCam grism transit.

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
\caption{Model spectra divided up by molecule for HD209458b. The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either of NIRCam's F322W2 or F444W slitless grism observations in its long wavelength arm. The error bars are for two DHS grism spectra taken simultaneously with each of the long wavelength grism observations. The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:DHSmolecules}
\end{figure}

Since the DHS was not originally designed for science observations, it is not yet an approved mode for the James Webb Space Telescope. In this white paper, we argue for the inclusion of the DHS mode to fully take advantage of two NIRCam arms to maximize JWST's science potential for transiting planets. In section \ref{sec:implementation}, we discuss how the DHS would work in for time series observations and the implications of reading out several detectors simultaneously at a high frame rate. In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.

@@

A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short wavelength arm and one spectrum on the long wavelength arm -- see Figure \ref{fig:DHSimage}. The 10 separate DHS spectra are spread across two of NIRCam's short wavelength detectors. Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source. Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on whether they lie in comparison to the secondary mirror strut supports seen in Figure \ref{fig:DHSvsPupilOverlay}. Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum. For sub-array sizes encompassing 1 DHS spectra, the large unobscured DHS grisms should be used like numbers 2, 4, 7 or 9.

%The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs. The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m. If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
\caption{Example images of the same source observed with the DHS on the short wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long wavelength arm (right). These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard. Only 3 detectors will be needed for transit observations.}\label{fig:DHSimage}
\end{figure}

\begin{table}
\centering
\begin{tabular}{cc}
DHS  Resolution &  R $\sim$ \DHSres \\
Dispersion & 0.29 nm / px \\
Wavelength Range & 1$\mu$m to 2$\mu$m, 0.05$\mu$m gap \\
Plate Scale & 32 mas/px \\
\hline \hline
Grism Resolution & R $\sim$ 1770 \\
Dispersion & 1.0 nm / px  \\
Wavelength Range F322W2 & 2.44$\mu$m to 4.02$\mu$m \\
Wavelength Range F444W & 3.88$\mu$m to 4.98 $\mu$m \\
Plate Scale & 65 mas/px \\
\end{tabular}
\caption{Properties of DHS and simultaneous long wavelength grism spectra.}\label{tab:DHSgprop}
\end{table}

@@

Each NIRCam array must be read out with identical window sizes and exposure times (due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}). This means that some balance must be made between saturating grism spectra (which has much higher throughput) in the long wavelength and getting the most flux in the short wave DHS spectrum (which has lower throughput and also spreads the light over more pixels).

The balance between saturating the long wavelength grism and getting enough signal to noise in the DHS is listed in Table \ref{tab:SatSNRsubA}. The table shows the brightest observable G2V star  for a given array size in the long wavelength grism and the signal to noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration. We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} is used and we consider 80\% well depth in the second read as saturation.

@@

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{example_ap_sizes.png}
\caption{Example sub-array size options for one of the short wavelength detectors for the DHS.}\label{fig:DHSaps}
\end{figure}

@@

There are a few ways to reduce the data volume streaming from the detectors. One way is to read each detector with a single amplifier (WINDOW mode). This reduces the frame rate by a factor of four (for the four amplifiers), thus allowing $\sim$40 hours before filling JWST's solid state recorders. The lower frame rate, however, means that the detector saturates at 1/4 the flux as four amplifiers. Second, the detector can be read out in BRIGHT1 mode, seen in Figure \ref{fig:readout}. This is where each a frame is dropped between read 2 and read 1 to increase the integration time while reducing data volume. This only works for sources faint enough that the long wavelength grisms do not saturate. Reducing the size of the sub-array does not affect the data volume because it just increases the number of frames so that approximately the same amount of data in pixels is saved to JWST's solid state recorder.

@@

The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST. Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long wavelength grisms. Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4. The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS).

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star. The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.}\label{fig:DHSaps}
\end{figure}

@@

We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long wavelength grisms. We first simulate a forward model of a transmission spectrum for a planet (in this case HD 209458b). We then add Gaussian noise using the signal to noise estimated on the target to create a simulated spectrum. Finally, we run an Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}. We combine the individual gases' posterior distributions for the C/O ratio and metallicity.

@@

For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m. We assume that each of these was accompanied by a DHS spectrum for the 1.01$\mu$ to 2.0$\mu$m wavelength range, which benefits in signal to noise by $\sqrt(2)$ for the two separate observations. This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra. The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short wavelength DHS observations. The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher signal to noise and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.

@@

One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances. A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor. However, the retrieval for the spectrum with only NIRCam's long wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}. Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.

@@

The James Webb Space Telescope will provide unprecedented measurements of transiting exoplanets, especially for carbon-bearing gases in their atmospheres. The time needed to observe in JWST's full range of wavelengths from 0.6$\mu$m to 28$\mu$m, however, can add up quickly since many transits are needed with different instrument modes to cover all wavelengths. We introduced a new science mode using the Dispersed Hartmann Sensor's on the NIRCam instrument which enable simultaneous measurements of spectra at R $\sim$ \DHSres\ from 1.0 to 2.0$\mu$m while using the NIRCam long wavelength grisms covering either 2.4$\mu$m to 4.0$\mu$m or 3.9$\mu$m to 5.0$\mu$m. The readout mode and subarray size much be chosen carefully on the DHS so as to not saturate the long wavelength grisms.

>>>>

\title{Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor}

@@

\author{E. Schlawin \and M. Rieke? \and J. Leisenring \and  L. M. Walker  \and J. Fraine? \and D. Kelly \and K. Misselt}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

@@

\begin{abstract}
James Webb Space Telescope (JWST) offers unprecedented sensitivity, stability and wavelength coverage for transiting exoplanet studies, opening up new avenues for measuring atmospheric abundances, structure and temperature profiles. Taking full advantage of JWST spectroscopy of planets from 0.6 $\mu$m to 28$\mu$m, however, will require many observations with a combination of the NIRISS, NIRCam, NIRSpec and MIRI instruments. In this white paper, we discuss a new NIRCam mode (not yet approved and implemented) that can reduce the number of observations needed for observations in the 1.0$\mu$m to 5.0$\mu$m wavelength range. The NIRCam instrument was primarily designed as an imager, but includes several grisms for phasing and aligning JWST's 18 hexagonal mirror segments. NIRCam's long-wavelength arm includes grisms that cover 2.4$\mu$m to 5.0$\mu$m with two observations at $R \sim 1770$ and it has already been approved for wide field slitless spectroscopy. We propose a new mode that will simultaneously measure spectra for science targets in the 1.0$\mu$m to 2.0$\mu$m range using NIRCam's short-wavelength arm. This mode, if approved, would take advantage of NIRCam's Dispersed Hartmann Sensor (DHS), which produces 10 spectra for every source at $R \sim \DHSres$. The DHS can observe the brightest host stars of any JWST mode. We discuss the added benefit of the DHS in constraining abundances in exoplanet atmospheres. The DHS essentially comes for free with any NIRCam long-wavelength grism observation, but the readout has to be selected to ensure that the long-wavelength grism observations do not saturate and that the high frame rate images on 3 simultaneous detectors does not exceed the data volume JWST can downlink. Combining both of NIRCam's arms will maximize the science potential of JWST, which is a limited life observatory.
\end{abstract}

@@

The James Webb Space Telescope (JWST) \citep[e.g.][]{gardner2006SSRv} has the potential to profoundly expand and deepen the science of transiting exoplanets \citep[e.g.][]{greene2016jwst_trans}. The wavelength coverage from 0.6$\mu$m to 28$\mu$m adds significantly to the wavelengths covered by the Hubble Space Telescope (HST) (currently 0.09$\mu$m to 1.7$\mu$m). Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent observatory for characterizing the atmospheres of planets that transit their host stars with time series observations. Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}. JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to it host star. Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes.

No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum. The largest bandwidths possible are NIRSpec's low resolution prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m. Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments. For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7 $\mu$m to 12 $\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7 to 2.5$\mu$m), two with NIRCam's long-wavelength arm (2.44$\mu$m to 4.98 $\mu$m) \footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m). With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours. This was calculated with the Astronomer's Proposal Tools software\footnote{http://www.stsci.edu/hst/proposing/apt} with the NIRISS SOSS mode, NIRCam's F322W2 and F444W grism time series and the MIRI Low Resolution spectrograph (LRS).

The NIRCam instrument is primarily an imager, but it includes several spectroscopic modes originally designed for wavefront sensing. These include the grisms installed in its long-wavelength arm as well as the Dispersed Hartmann Sensors (DHSs) installed in its short-wavelength arm. The long-wavelength grisms are used in concert with broadband filters. The F322W2 filter encompasses 2.44$\mu$m to 4.02$\mu$m half maximum throughput while the F444W filter encompasses 3.88$\mu$ to 4.98$\mu$m at half maximum throughput. These filters and grism are enabled and supported JWST science modes. The DHS would be used primarily with the F150W2 filter, which covers from 1.01$\mu$m to 2.35$\mu$m at half maximum throughput. The range from 2.0$\mu$m to 2.35$\mu$m will probably be discarded because the first order of the spectrum begins to overlap at at 2.0$\mu$m.

The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5 $\mu$m. This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength arm and long-wavelength arm, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths. In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter. Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}. For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0 to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required. The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
\caption{Model spectra divided up by molecule for HD209458b. The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm. The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra. The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:DHSmolecules}
\end{figure}

Since the DHS was not originally designed for science observations, it is not yet an approved mode for the James Webb Space Telescope. In this white paper, we argue for the inclusion of the DHS mode to fully take advantage of two NIRCam arms to maximize JWST's science potential for transiting planets. In section \ref{sec:implementation}, we discuss how the DHS would work for time-series observations and the implications of reading out several detectors simultaneously at a high frame rate. In section \ref{sec:addedScience} we discuss the added science that can be achieved with the DHS, including the brightness limits and improved precision in retrieved parameters for a representative system.

@@

A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength arm and one spectrum on the long-wavelength arm -- see Figure \ref{fig:DHSimage}. The DHS mode is only well suited for one source at a time because of the large number of spectra that would overlap in a crowded field. The 10 separate DHS spectra are spread across two of NIRCam's short-wavelength detectors. Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source. Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports seen in Figure \ref{fig:DHSvsPupilOverlay}. Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum. For sub-array sizes encompassing 1 DHS spectra, the large unobscured DHS grisms should be used like numbers 3, 7 or 9.

%The two DHS pupil configurations include 10 prisms spanning adjoining edges of JWST's hexagonal mirrors, at 60 degrees from each other to encompass different mirror pairs. The resulting image, shown in Figure \ref{fig:DHSimage} is that 10 separate spectra are produced for every point source covering the wavelengths from 1$\mu$m to 2$\mu$m. If two JWST mirrors are misaligned, they will produce a ``barber pole''-shaped interference pattern on the array.
\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{dhs_image_example.png}
\caption{Example images of the same source observed with the DHS on the short-wavelength arm (left) producing 10 spectra and the F444W filter and C grism on the long-wavelength arm (right). These images were taken during cryogenic vacuum testing of the NIRCam flight instrument and detectors at NASA Goddard. Only 3 detectors will be needed for transit observations.}\label{fig:DHSimage}
\end{figure}

\begin{table}
\centering
\begin{tabular}{ccc}
 &  R $\sim$ \DHSres \\
 \hline \hline
Dispersion & 0.29 nm / px \\
Wavelength Range & 1$\mu$m to 2$\mu$m, 0.05$\mu$m gap \\
Plate Scale & 32 mas/px \\
\hline \hline
Grism Resolution & R $\sim$ 1770 \\
Dispersion & 1.0 nm / px  \\
Wavelength Range F322W2 & 2.44$\mu$m to 4.02$\mu$m \\
Wavelength Range F444W & 3.88$\mu$m to 4.98 $\mu$m \\
Plate Scale & 65 mas/px \\
\end{tabular}
\caption{Properties of DHS and simultaneous long-wavelength grism spectra.}\label{tab:DHSgprop}
\end{table}

@@

Each NIRCam array must be read out with identical window sizes and exposure times (due to restrictions in the Onboard Scripting Software (OSS) (\textbf{and the SSR?}). This means that some balance must be made between saturating grism spectra (which has much higher throughput) in the long-wavelength and getting the most flux in the short wave DHS spectrum (which has lower throughput and also spreads the light over more pixels).

The balance between saturating the long-wavelength grism and getting enough signal to noise in the DHS is listed in Table \ref{tab:SatSNRsubA}. The table shows the brightest observable G2V star  for a given array size in the long-wavelength grism and the signal to noise at 1.5$\mu$m for a G2V type star at this brightness observing a 1 hour long transit duration. We use the standard correlated double sampling (CDS) readout mode shown in Figure \ref{fig:readout} is used and we consider 80\% well depth in the second read as saturation.

@@

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{example_ap_sizes.png}
\caption{Example sub-array size options for one of the short-wavelength detectors for the DHS. Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay}}\label{fig:DHSaps}
\end{figure}

@@

There are a few ways to reduce the data volume streaming from the detectors. One way is to read each detector with a single amplifier (WINDOW mode). This reduces the frame rate by a factor of four (for the four amplifiers), thus allowing $\sim$40 hours before filling JWST's solid state recorders. The lower frame rate, however, means that the detector saturates at 1/4 the flux as four amplifiers. Second, the detector can be read out in BRIGHT1 mode, seen in Figure \ref{fig:readout}. This is where each a frame is dropped between read 2 and read 1 to increase the integration time while reducing data volume. This only works for sources faint enough that the long-wavelength grisms do not saturate. Reducing the size of the sub-array does not affect the data volume because it just increases the number of frames so that approximately the same amount of data in pixels is saved to JWST's solid state recorder.

@@

The DHS has the best brightness limits of any spectroscopic mode on JWST because it spreads light over many pixels and reduces the effective aperture of JWST. Figure \ref{fig:DHSaps} shows the saturation limits for the DHS mode along with NIRCam's long-wavelength grisms. Any known transiting planet host system can be observed with the DHS, including the transiting super-Earth  55 Cnc e \citep{mcarthur2004disc55cnce} at $K$=4.0, which is right at the limit of saturation of the long-wavelength grism and the brightest known transiting system HD 219134b \citep{motalebi2015hd219134b} at $K$=3.4. The DHS also enables characterization of any future targets found in this brightness range, such as by the Transiting Exoplanet Survey Satellite (TESS).

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star. The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.}\label{fig:DHSaps}
\end{figure}

@@

We use the CHIMERA atmospheric retrieval suite \citep{line2013chimera,line2014CtOsecE} to show the scientific value of using the DHS simultaneously with NIRCam's long-wavelength grisms. We first simulate a forward model of a transmission spectrum for a planet (in this case HD 209458b). We then add Gaussian noise using the signal to noise estimated on the target to create a simulated spectrum. Finally, we run an Markov Chain Monte Carlo (MCMC) retrieval of the atmospheric parameters for simulated spectrum to try to recover the initial abundances and determine the uncertainties in those abundances, as in \citet{greene2016jwst_trans}. We combine the individual gases' posterior distributions for the C/O ratio and metallicity.

@@

For the simulated observations, we assume one transit is obtained in each of NIRCam's long-wavelength filters (F322W2 and F444W) to cover the wavelength range from 2.44$\mu$m to 4.99$\mu$m. We assume that each of these was accompanied by a DHS spectrum for the 1.01$\mu$ to 2.0$\mu$m wavelength range, which benefits in signal to noise by $\sqrt(2)$ for the two separate observations. This is compared to observations taken without the DHS to show the added scientific value of using the DHS spectra. The noise models for the hot Jupiter HD 209458b are shown in Figure \ref{fig:DHSvsNIRISS209}, which is dominated by the detector noise floor (35 ppm) for the long-wavelength grisms ($>$2.44$\mu$m) but photon noise is more significant for the short-wavelength DHS observations. The DHS has lower throughput and a smaller wavelength coverage than the NIRISS instrument in SOSS mode, so observations which require higher signal to noise and full wavelength coverage from 0.7 to 2.4$\mu$m can take advantage of NIRISS (also shown in Figure \ref{fig:DHSvsNIRISS209}) at the expense of more telescope time.

@@

One of the surprising aspects to the retrievals is that the DHS improves both the constraints on the CO and CO$_2$ abundances as well as the H$_2$O abundances. A quick glance at the contributions of individual molecules to the spectrum shown in Figure \ref{fig:DHSmolecules} would indicate that the DHS is mainly important for water vapor. However, the retrieval for the spectrum with only NIRCam's long-wavelength grisms has a strong correlation between the retrieved H$_2$O abundances with CO$_2$ and CO, shown in Figure \ref{fig:cornerRun}. Improving the water vapor constraint with the DHS, reduces the correlation and therefore improves the abundance constraints for all three.

@@

The James Webb Space Telescope will provide unprecedented measurements of transiting exoplanets, especially for carbon-bearing gases in their atmospheres. The time needed to observe in JWST's full range of wavelengths from 0.6$\mu$m to 28$\mu$m, however, can add up quickly since many transits are needed with different instrument modes to cover all wavelengths. We introduced a new science mode using the Dispersed Hartmann Sensor's on the NIRCam instrument which enable simultaneous measurements of spectra at R $\sim$ \DHSres\ from 1.0 to 2.0$\mu$m while using the NIRCam long-wavelength grisms covering either 2.4$\mu$m to 4.0$\mu$m or 3.9$\mu$m to 5.0$\mu$m. The readout mode and subarray size much be chosen carefully on the DHS so as to not saturate the long-wavelength grisms.
